Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-19 ms.tex
may have finished first pass at full description of noise model

\begin{equation}
\Sigma = \begin{pmatrix} \sigma^2_{217}                           & \ldots  & \rho_{217,3000}\sigma_{217}\sigma_{3000} \\ 
                         \vdots                                   & \ddots  & \vdots                                   \\
                         \rho_{3000,217}\sigma_{3000}\sigma_{217} & \ldots  & \sigma^2_{3000}
\end{pmatrix}
\end{equation}

@@

% still need to explain off-diagonal terms in covariance ...

@@

\subsection{Rectifying the Reddening Residuals}
In this section we describe our attempts to eliminate the systematic
problems in the two-component reddening residuals shown in the left column
of Figure \ref{fig:resid}. We employed two main strategies: (1) recomputing
the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
the input maps and/or changing the particular two-component model adopted and
(2) making spatial cuts to isolate sky regions in which the 
residuals are especially pristine (or especially problematic).

>>>>

\begin{equation} \label{equ:covariance}
\Sigma = \begin{pmatrix} \sigma^2_{217}                           & \ldots  & \rho_{217,3000}\sigma_{217}\sigma_{3000} \\ 
                         \vdots                                   & \ddots  & \vdots                                   \\
                         \rho_{3000,217}\sigma_{3000}\sigma_{217} & \ldots  & \sigma^2_{3000}
\end{pmatrix}
\end{equation}

@@

Finally, we include a term to account for the RMS amplitude of the CIBA in
band $\nu_i$, $\sigma_{CIBA, \nu_i}$. The values for the CIBA RMS amplitudes 
are obtained by assuming a $T$=18.3 K, $\beta$=1.0 MBB spectrum for the CIB, 
with 857 GHz normalization from \cite{ciba}. The CIBA not only contributes to 
the per-band variance $\sigma^2_{\nu_i}$, but also to the inter-frequency 
covariances; this is why we have included the off-diagonal terms in the
covariance matrix of Equation \ref{equ:covariance}. In our noise model, the 
CIBA is the only source of inter-frequency covariance. Thus, the off-diagonal 
covariance matrix element between bands $\nu_i$ and $\nu_j$ is given by:

\begin{equation}
\Sigma_{ij} = \rho_{\nu_i, \nu_j}\sigma_{\nu_i}\sigma_{\nu_j} = \rho_{CIBA, \nu_i, \nu_j}\sigma_{CIBA, \nu_i}\sigma_{CIBA, \nu_j}
\end{equation}

With values for $\rho_{CIBA, \nu_i, \nu_j}$ from \cite{covarciba}. The approach
we have taken in accounting for the CIBA is similar to that of 
\cite{planckdust}, Appendix B, in that we treat the CIBA amplitude in each 
pixel as a Gaussian random draw. However, instead of performing a separate 
analysis to gauge the uncertainty on derived dust parameters due to the CIBA, 
we allow the CIBA covariance to propagate naturally into our uncertainties via 
the likelihood function. Still, our treatment of the CIBA is a major 
oversimplification relative to the ideal situation in which the detailed 
spatial structure of the CIBA would be thoroughly accounted for or even removed
by subtraction.

@@

\subsection{Rectifying the Reddening Residuals}

In this section we describe our attempts to eliminate the systematic
problems in the two-component reddening residuals shown in the left column
of Figure \ref{fig:resid}. We employed two main strategies: (1) recomputing
the two-component $\tau_{545}$ by re-running our Markov chains after modifying 
the input maps and/or changing the particular two-component model adopted and
(2) making spatial cuts to isolate sky regions in which the 
residuals are especially pristine (or especially problematic).
